Tabular Constraint Learning

### 2016-04-08 Paper/ECAI/tabular.tex
refactoring the paper

\sergey{to himself we need structure here} 
\begin{figure}[thpb]
  \begin{center}
    \includegraphics[width=0.51\textwidth]{figures/Demo.png}
  \end{center}
  \vspace{-10pt}
  \caption{An example of constraint reconstruction (in blue) with indicated groups (in green)}
  \label{fig:main_example}
\end{figure}

@@

An \textit{Excel constraint} is a triple \textit{(\CName, \CSignature, \CFunction)}, where \textit{\CName} is a textual name of the constraint; \textit{\CSignature} is a set of constraints specifying the properties of the arguments, such as their types, e.g., to require them to be integers or sizes, e.g. the length of vectors in the arguments must be equal, i.e., these are constraints on the group meta-information not on the actual group content; \textit{\CFunction} is a set of constraints specifying that the data in the subgroups satisfies the function. For example, an excel constraint \textit{rank} has \CName \textit{Y = RANK(X)}; its \CSignature is: the group $G_X$ (associated with X) is numeric, $G_Y$ is integer and the length of vectors in $G_X$ is the same as in $G_Y$; its \CFunction is the following constraint: a pair of vectors $X,Y$ is a solution iff $X \in G_X, Y \in G_Y$ and each value in $X$ has the rank (possibly with ties) specified in $Y$.

\subsection{Constraint learning algorithm description}
Let us describe the key steps and functions in Algorithm \ref{algo:tcl}. Essentially, the algorithm has two steps: candidate group generation and subgroup satisfaction search, which is in line with the ``generate-and-test'' paradigm that is well-known in AI \cite{whaisasp}. Let us elaborate on each step in detail.

>>>>

\sergey{need to elaborate the example here: like in a story}

\begin{figure*}[tbh]
  \begin{center}
    \includegraphics[width=0.75\textwidth]{figures/Demo.png}
  \end{center}
  \vspace{-10pt}
  \caption{An example of constraint reconstruction (in blue) with indicated groups (in green)}
  \label{fig:main_example}
\end{figure*}

@@

An \textit{Excel constraint} is a triple \textit{(\CName, \CSignature, \CFunction)}. Let us elaborate on each of them. \textit{\CName} is the textual name of the constraint together with its variable names. \textit{\CSignature} is a set of constraints specifying the properties of the group assignments, corresponding to the variables in \CName, such as their types, e.g., requiring them to be integers or constraining the sizes, e.g. the length of vectors in the arguments must be equal. These are constraints on the group meta-information not on the actual group content. \textit{\CFunction} is a set of constraints specifying that the data in the subgroups satisfies the function. For example, an excel constraint \textit{rank} has \CName \textit{Y = RANK(X)}, where $X$ and $Y$ are the variables; its \CSignature is: the group $G_X$ (associated with X) is numeric, $G_Y$ is integer and the length of vectors in $G_X$ is the same as in $G_Y$; its \CFunction is the following constraint: a pair of vectors $X,Y$ is a solution iff $X \in G_X, Y \in G_Y$ and each value in $X$ has the rank (possibly with ties) specified in $Y$.

\section{Problem Statement}

\section{Approach to Tabular Constraint Learning}
Let us describe the key steps and functions in Algorithm \ref{algo:tcl}. Essentially, the algorithm has two steps: candidate group generation and subgroup satisfaction search, which is in line with the ``generate-and-test'' paradigm that is well-known in AI \cite{whaisasp}. Let us elaborate on each step in detail.
